---
title: "Comparison of TB CXR diagnoses between different readers"
author: " Bernard Melingui & Samuel Beneteau"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
    fig_caption: yes
    fig_width: 8
    fig_height: 4
  
vignette: "%\\VignetteIndexEntry{CXR} %\\VignetteEngine{knitr::rmarkdown} %\\VignetteEncoding{UTF-8}\n"
link-citations: yes
linkcolor: blue

knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                    encoding=encoding, 
                    output_file=paste(Sys.Date(),"_analysis.html", sep=""),
                    output_dir="output/")})
---

<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include = FALSE}
#bibliography: Citation.bib
knitr::opts_chunk$set(
  collapse = TRUE,
  warning=F,
  message=F,
  comment = "#>"
)
```


# Introduction

Analyse réalisée avec R [@R-citation], les packages utilisés sont les suivants :

```{r, echo=F}
library(readxl)
library(data.table)
library(car)
library(forcats)
library(lme4)
library(caret)
library(gtsummary)
library(dplyr)
library(performance)
library(MuMIn)
library(knitr)
library(binom)
library(epiR)
library(kableExtra)
library(flextable)
```

# Import des fichiers

```{r, echo=F}
dt.one <- read_excel("data/CXR_Reading_clinician_vs_national Reader.20230803.xlsx")
dt.one <- as.data.table(dt.one)

dt.two <- read_excel("data/CXR_Reading_clinician_vs_SPI.xlsx")
dt.two <- as.data.table(dt.two)

#table(dt.one$NationalReader.result)
```

# Jointure

```{r, echo=F}
dt.two <- dt.two[, c("Patient ID", "SPI.quality", "SPI.result", "SPI.alveolar_opacity", "SPI.miliary", "SPI.cavitation",
                     "SPI.enlarged_lymph_nodes","SPI.airway_compression", "SPI.pleural_effusion"), with=F]

dt.final <- dt.one[dt.two, on="Patient ID"]

rm(dt.one, dt.two)

#lapply(dt.final, unique)
```


# Pré-traitement

```{r, echo=F}
dt.final$CXR_DAT <- NULL  
dt.final[dt.final == "acceptable"] <- "Acceptable"

dt.final[dt.final == "unacceptable"] <- "Unacceptable"

dt.final[dt.final == "not suggestive of TB"] <- "Not suggestive of TB"
dt.final[dt.final == "no"] <- "No"
dt.final[dt.final == "yes"] <- "Yes"
dt.final[dt.final == "NO"] <- "No"
dt.final[dt.final == "not readable"] <- "Not readable"
dt.final[dt.final == "suggestive of TB"] <- "Suggestive of TB"
dt.final[dt.final == "readable"] <- "Readable"
dt.final[dt.final == "Not suggested of TB"] <- "Not suggestive of TB"
dt.final[dt.final == "Suggested of TB"] <- "Suggestive of TB"

dt.final[dt.final == "NR"] <- "Not readable"
dt.final[dt.final == "missing"] <- NA

for(i in c("acceptable*","acepptable","aceptable")){
  dt.final[dt.final == i] <- "Acceptable"
}

for(i in c("non acceptable","Not acceptable","uacceptable", "unacceptaéble","unaccept", "inacceptable",
           "not acceptable ", "not acceptable")){
  dt.final[dt.final == i] <- "Unacceptable"
}


for(i in c("not suggested", "not  suggested", "not suggestive", "not ssuggestive of tb", "not sug",
           "not ssuggestive", "not suggest.", "not sugg", "not sugget", "not suggest", "not sugges",
           "not suggestive of tb", "not suggestiveof tb", "not suggesytive","Not suggestive of Tb",
           "not suggestive*", "not suggestve", "Not Suggestive of TB")){
  dt.final[dt.final == i] <- "Not suggestive of TB"
}


for(i in c("suggested of TB", "suggest of tb", "suggest*", "suggestive otb", "suggestive of tb",
           "suggestive*","suggestive","suggestive of tb**","suggestive of Tb","sugestive of tb",
           "suggestiveof TB", "suggestiveof tb", "sugges of tb")){
  dt.final[dt.final == i] <- "Suggestive of TB"
}

for(i in c("not redeable", "not readable ( ?inspiration )", "Not read")){
  dt.final[dt.final == i] <- "Not readable"
}


dt.final[NationalReader.result == "Unacceptable", NationalReader.result := NA]
dt.final[NationalReader.quality == "Missing", NationalReader.quality := NA]

#lapply(dt.final, unique)
```


```{r, echo=F}
dt.final <- melt(dt.final,
                 id.vars =c("Patient ID", "Country", "DISTRICT", "read_number"),
                 measure.vars=c("Clinician.quality","Clinician.result", "SPI.quality", "SPI.result", "NationalReader.quality",
                                "NationalReader.result","Clinician.alveolar_opacity","NationalReader.alveolar_opacity",
                                "Clinician.miliary","NationalReader.miliary","Clinician.cavitation","NationalReader.cavitation",
                                "Clinician.enlarged_lymph_nodes","NationalReader.enlarged_lymph_nodes","Clinician.airway_compression",
                                "NationalReader.airway_compression","Clinician.pleural_effusion","NationalReader.pleural_effusion",
                                "SPI.alveolar_opacity", "SPI.miliary", "SPI.cavitation", "SPI.enlarged_lymph_nodes",
                                "SPI.airway_compression","SPI.pleural_effusion")
)

dt.final[, c("Readers", "Signs") := tstrsplit(variable, split=".", fixed = T)]

fwrite(dt.final, "data/base_finale.csv")
#table(dt.final$Clinician.result)
```

# Analyse

```{r}
dt.final <- fread("data/base_finale.csv")
```

## Radiographies description

```{r}
q <- dt.final[Readers == "Clinician" & (Signs != "quality" & Signs != "result")] %>%
  dcast(`Patient ID` + Country + read_number ~ Signs,
        value.var = "value",
        fun.aggregate = function(x){sum(x == "Yes", na.rm=T)})

q[q == 1] <- "Yes"
q[q == 2] <- "Yes"
q[q == 0] <- "No"
```


```{r}
q %>%
  tbl_summary(
    include=-c("Patient ID", "Country"),
    by = read_number,
    type = everything() ~ "categorical",
    statistic = all_categorical() ~ "{p} % ({n}/{N})",
    missing="ifany"
  ) %>% add_overall(last=T)
```

```{r}
q2 <- dt.final[Readers == "Clinician" & Signs == "result"]
q3 <- dt.final[Readers == "Clinician" & (Signs != "quality" & Signs != "result")]
q2 <- q2[q3, on=c("Patient ID", "Country", "Readers", "read_number")]

q2 <- dcast(q2, `Patient ID` + read_number + value ~ i.Signs,
        value.var = "i.value",
        fun.aggregate = function(x){sum(x == "Yes", na.rm=T)})

q2[q2 == 0] <- "No"
q2[q2 == 1] <- "Yes"
q2[q2 == 4] <- "Yes"

a<- q2 %>%
  tbl_strata(
    strata = read_number,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = value,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ " {n} ({p} %)",
        missing="ifany"
      ))
a
#save_as_docx(a %>% as_flex_table(), path = "table_descr.docx")
```

## Clinician versus SPI

### By Signs

```{r, echo=F, fig.show='hold'}
c <- dt.final[Signs != "quality"][value != "Not readable"]
c <- dcast(c, `Patient ID`+ Signs ~ Readers, value.var = "value", fun.aggregate = unique, fill=NA)
c <- c[, .(`Patient ID`, Signs, Clinician, SPI)]
```

#### Contingency table

```{r, echo=F}
b <- c[Signs != "result"]

by.sign <- b %>%
  tbl_strata(
    strata = Signs,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = SPI,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))

all.sign <- b[, Signs:="All"] %>%
  tbl_strata(
    strata = Signs,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = SPI,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))

tbl_merge(list(all.sign, by.sign), tab_spanner = F)
```


#### Performances with epi package

```{r, echo=F}
c.sign <- c[Signs != "result"]
c.sign[, Clinician := factor(Clinician, levels=c("Yes", "No"))]
c.sign[, SPI := factor(SPI, levels=c("Yes", "No"))]

all.sign <- list(
  table(c.sign$Clinician, c.sign$SPI)
  )

by.sign <- lapply(unique(c.sign$Signs), function(x){
  table(c.sign[Signs == x]$Clinician, c.sign[Signs == x]$SPI)
})

result <- lapply("result", function(x){
  c <- c[Signs == x]
  c[, Clinician := factor(Clinician, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  c[, SPI := factor(SPI, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  table(c$Clinician, c$SPI)
})

b <- c(all.sign, by.sign, result)

names(b) <- c("All", unique(c.sign$Signs), "result")
```


```{r, echo=F}
b.res <- lapply(b, epi.tests, conf.level = 0.95, method = "clopper-pearson")

b.res <- lapply(b.res, function(x){
  q <- as.data.table(x$detail)
  q <- q[, lapply(.SD, round, 2), by= .(statistic)]
  q 
})

b.res <- lapply(b.res, function(x){
  x[, all := paste(est, " [", lower, "-", upper, "]", sep="")]
})


b.res <- rbindlist(b.res, idcol = T)

dcast(b.res, statistic ~ .id, value.var = "all") %>% kable %>% kable_styling
```

```{r}
c.res <- lapply(b, epi.kappa)

c.res <- lapply(c.res, rbindlist, fill=T, idcol="param")

c.res <- c.res %>% rbindlist(idcol=T) %>%
  .[param %in% c("pabak", "kappa")] %>%
  .[, .(.id, param, est = round(est, 2), lower = round(lower, 2), upper = round(upper, 2))]

c.res[, all := paste(est, " [", lower, "-", upper, "]", sep="")]

dcast(c.res, param ~ .id, value.var = "all") %>% kable %>% kable_styling
```


### By Signs and Country

```{r, echo=F}
dt.country <- dt.final[Signs != "quality"][value != "Not readable"]

dt.country.sign <- dt.country[Signs != "result"] %>% dcast(`Patient ID`+ Country + Signs ~ Readers,
                                                           value.var = "value",
                                                           fun.aggregate = unique,
                                                           fill=NA)

dt.country.sign <- dt.country.sign %>% dcast(`Patient ID`+ Country + SPI ~ Signs,
                                             value.var = "Clinician",
                                             fun.aggregate = unique,
                                             fill=NA)

dt.country.sign %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = SPI,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))
```

```{r, echo=F}
dt.country.result <- dt.country[Signs == "result"] %>% dcast(`Patient ID`+ Country + Signs ~ Readers,
                                                             value.var = "value",
                                                             fun.aggregate = unique,
                                                             fill=NA)

dt.country.result <- dt.country.result %>% dcast(`Patient ID`+ Country + SPI ~ Signs,
                                                 value.var = "Clinician",
                                                 fun.aggregate = unique,
                                                 fill=NA)

dt.country.result %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = SPI,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))
```


```{r echo=F, message=FALSE, warning=FALSE}
dt.country.reader <- dt.country %>%  dcast(`Patient ID`+ Country + Signs + read_number ~ Readers,
                                           value.var = "value",
                                           fun.aggregate = unique,
                                           fill=NA)

a <- unique(dt.country.reader[, .(Country, Signs)])
e <- unique(dt.country.reader[, .(read_number, Signs)])

list.tbl <- lapply(1:nrow(a), function(x){
  dt.temp <- dt.country.reader[Country == a$Country[[x]] & Signs == a$Signs[[x]]]
  dt.temp[, Clinician := factor(Clinician, levels = rev(sort(unique(Clinician))))]
  dt.temp[, SPI := factor(SPI, levels = rev(sort(unique(SPI))))]
  table(dt.temp$Clinician, dt.temp$SPI)
})

list.tbl <- lapply(list.tbl, epi.tests, conf.level = 0.95, method = "clopper-pearson")

list.tbl <- lapply(list.tbl, function(x){ as.data.table(x$detail) })

result.country <- rbindlist(list.tbl)

result.country[, Country := rep(a$Country, each=18)]
result.country[, Signs := rep(a$Signs, each=18)]

result.country[, ci := paste(round(est, 2), " [", round(lower, 2), "-", round(upper, 2), "]", sep="")]

dcast(result.country, statistic + Country ~ Signs, value.var = "ci") %>% kable %>% kable_styling
```


```{r, echo=F}
w <- result.country[Signs != "result" & statistic %in% c("se", "sp")][order(Country)]
w <- result.country[Signs != "result" & statistic %in% "se"][order(Country)]

ggplot(data=w, aes(x= Country, fill=Signs, y=est)) +
  geom_bar(stat="identity",position = "dodge")+
   scale_fill_brewer(palette="Paired")+
  theme_minimal() +
  scale_fill_grey() +
  ylab("Sensitivity")
w1 <- result.country[Signs != "result" & statistic %in% "sp"][order(Country)]

ggplot(data=w1, aes(x= Country, fill=Signs, y=est)) +
  geom_bar(stat="identity",position = "dodge")+
   scale_fill_brewer(palette="Paired")+
  theme_minimal() +
  scale_fill_grey() +
  ylab("Specificity")

```


```{r, echo=F}
w <- result.country[Signs == "result" & statistic %in% c("se", "sp")][order(Country)]

dt.bp <- dcast(w, statistic ~ Country, value.var="est")
dt.bp <- as.matrix(dt.bp, rownames=T)

ci.w <- 0.05

par(mar=c(2, 5, 2, 5), xpd=T)
bp <- barplot(dt.bp, ylab="Value", cex.names=0.8, ylim=c(0,1), beside=T, col=c("gray", "grey50"))

legend("right",
       legend = c("Sensibility", "Specificity"),
       col=c("gray", "grey50"),
       pch = 15,
       bty = "n",
       pt.cex = 2,
       cex = 0.7,
       horiz = F, inset = c(-0.15, 0))

bp <- as.vector(bp)
segments(bp-ci.w, w$lower, bp+ci.w, w$lower, lwd = 1.5)
segments(bp-ci.w, w$upper, bp+ci.w, w$upper, lwd = 1.5)
segments(bp, w$lower, bp, w$upper, lwd = 1.5)
```

### Result by Read Number

```{r, echo=F}
c <- dt.final[Signs == "result"][value != "Not readable"]
c <- dcast(c, `Patient ID`+ read_number ~ Readers, value.var = "value", fun.aggregate = unique, fill=NA)
c <- c[, .(`Patient ID`, read_number, Clinician, SPI)]


w <- lapply(unique(c$read_number), function(x){
  c <- c[read_number == x]
  c[, Clinician := factor(Clinician, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  c[, SPI := factor(SPI, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  table(c$Clinician, c$SPI)
})

w <- lapply(w, epi.tests, conf.level = 0.95, method = "clopper-pearson")
names(w) <- unique(c$read_number)


w <- lapply(w, function(x){
  as.data.table(x$detail)
})

w <- rbindlist(w, idcol = T)
```

```{r, echo=F}
w <- w[statistic %in% c("se", "sp")]
w %>% kable %>% kable_styling
```

```{r, echo=F}
dt.bp <- dcast(w, statistic ~ .id, value.var="est")
dt.bp <- as.matrix(dt.bp, rownames=T)

ci.w <- 0.05

par(mar=c(2, 5, 2, 5), xpd=T)
bp <- barplot(dt.bp, ylab="Value", cex.names=0.8, ylim=c(0,1), beside=T, col=c("gray", "grey50"))

legend("right",
       legend = c("Sensibility", "Specificity"),
       col=c("gray", "grey50"),
       pch = 15,
       bty = "n",
       pt.cex = 2,
       cex = 0.7,
       horiz = F, inset = c(-0.15, 0))

bp <- as.vector(bp)
segments(bp-ci.w, w$lower, bp+ci.w, w$lower, lwd = 1.5)
segments(bp-ci.w, w$upper, bp+ci.w, w$upper, lwd = 1.5)
segments(bp, w$lower, bp, w$upper, lwd = 1.5)
```

```{r}
dt.bp <- as.data.table(t(dt.bp))
dt.bp[, x := 1:4]

lm(dt.bp$se ~ dt.bp$x) %>% summary

lm(dt.bp$sp ~ dt.bp$x) %>% summary
```

## Clinician versus National Reader

### By signs

```{r, echo=F}
c <- dt.final[Signs != "quality"][value != "Not readable"]
c <- dcast(c, `Patient ID`+ Signs ~ Readers, value.var = "value", fun.aggregate = unique, fill=NA)
c <- c[, .(`Patient ID`, Signs, Clinician, NationalReader)]
```

#### Contingency table

```{r, echo=F}
b <- c[Signs != "result"]

by.sign <- b %>%
  tbl_strata(
    strata = Signs,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))

all.sign <- b[, Signs:="All"] %>%
  tbl_strata(
    strata = Signs,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))

tbl_merge(list(all.sign, by.sign), tab_spanner = F)
```


#### Performances with epi package

```{r, echo=F}
c.sign <- c[Signs != "result"]
c.sign[, Clinician := factor(Clinician, levels=c("Yes", "No"))]
c.sign[, NationalReader := factor(NationalReader, levels=c("Yes", "No"))]

all.sign <- list(
  table(c.sign$Clinician, c.sign$NationalReader)
  )

by.sign <- lapply(unique(c.sign$Signs), function(x){
  table(c.sign[Signs == x]$Clinician, c.sign[Signs == x]$NationalReader)
})

result <- lapply("result", function(x){
  c = c[Signs == x]
  c[, Clinician := factor(Clinician, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  c[, NationalReader := factor(NationalReader, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  table(c$Clinician, c$NationalReader)
})

b <- c(all.sign, by.sign, result)

names(b) <- c("All", unique(c.sign$Signs), "result")
```


```{r, echo=F}
b.res <- lapply(b, epi.tests, conf.level = 0.95, method = "clopper-pearson")

b.res <- lapply(b.res, function(x){
  q <- as.data.table(x$detail)
  q <- q[, lapply(.SD, round, 2), by= .(statistic)]
  q 
})

b.res <- lapply(b.res, function(x){
  x[, all := paste(est, " [", lower, "-", upper, "]", sep="")]
})


b.res <- rbindlist(b.res, idcol = T)

dcast(b.res, statistic ~ .id, value.var = "all") %>% kable %>% kable_styling
```

```{r}
c.res <- lapply(b, epi.kappa)

c.res <- lapply(c.res, rbindlist, fill=T, idcol="param")

c.res <- c.res %>% rbindlist(idcol=T) %>%
  .[param %in% c("pabak", "kappa")] %>%
  .[, .(.id, param, est = round(est, 2), lower = round(lower, 2), upper = round(upper, 2))]

c.res[, all := paste(est, " [", lower, "-", upper, "]", sep="")]

dcast(c.res, param ~ .id, value.var = "all") %>% kable %>% kable_styling
```

### By Signs and Country

```{r, echo=F}
dt.country.sign <- dt.country[Signs != "result"] %>% dcast(`Patient ID`+ Country + Signs ~ Readers,
                                                           value.var = "value",
                                                           fun.aggregate = unique,
                                                           fill=NA)

dt.country.sign <- dt.country.sign %>% dcast(`Patient ID`+ Country + NationalReader ~ Signs,
                                             value.var = "Clinician",
                                             fun.aggregate = unique,
                                             fill=NA)

dt.country.sign %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))
```

```{r, echo=F}
dt.country.result = dt.country[Signs == "result"] %>% dcast(`Patient ID`+ Country + Signs ~ Readers,
                                                            value.var = "value",
                                                            fun.aggregate = unique,
                                                            fill=NA)

dt.country.result = dt.country.result %>% dcast(`Patient ID`+ Country + NationalReader ~ Signs,
                                                value.var = "Clinician",
                                                fun.aggregate = unique,
                                                fill=NA)

dt.country.result %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))
```



```{r, echo=F}
list.tbl <- lapply(1:nrow(a), function(x){
  dt.temp <- dt.country.reader[Country == a$Country[[x]] & Signs == a$Signs[[x]]]
  dt.temp[, Clinician := factor(Clinician, levels = rev(sort(unique(Clinician))))]
  dt.temp[, NationalReader := factor(NationalReader, levels = rev(sort(unique(NationalReader))))]
  table(dt.temp$Clinician, dt.temp$NationalReader)
})

list.tbl <- lapply(list.tbl, epi.tests, conf.level = 0.95, method = "clopper-pearson")

list.tbl <- lapply(list.tbl, function(x){ as.data.table(x$detail) })

result.country <- rbindlist(list.tbl)

result.country[, Country := rep(a$Country, each=18)]
result.country[, Signs := rep(a$Signs, each=18)]

result.country[, ci := paste(round(est, 2), " [", round(lower, 2), "-", round(upper, 2), "]", sep="")]

dcast(result.country, statistic + Country ~ Signs, value.var = "ci") %>% kable %>% kable_styling

```

# analyses by EQA and radiological lesions
```{r, echo=F}
list.tbl <- lapply(1:nrow(e), function(x){
  dt.temp <- dt.country.reader[read_number == e$read_number[[x]] & Signs == e$Signs[[x]]]
  dt.temp[, Clinician := factor(Clinician, levels = rev(sort(unique(Clinician))))]
  dt.temp[, NationalReader := factor(NationalReader, levels = rev(sort(unique(NationalReader))))]
  table(dt.temp$Clinician, dt.temp$NationalReader)
})

list.tbl <- lapply(list.tbl, epi.tests, conf.level = 0.95, method = "clopper-pearson")

list.tbl <- lapply(list.tbl, function(x){ as.data.table(x$detail) })

result.number <- rbindlist(list.tbl)

result.number[, read_number := rep(e$read_number, each=18)]
result.number[, Signs := rep(e$Signs, each=18)]

result.number[, ci := paste(round(est, 2), " [", round(lower, 2), "-", round(upper, 2), "]", sep="")]

dcast(result.number, statistic + read_number ~ Signs, value.var = "ci") %>% kable %>% kable_styling



```

```{r, echo=F}
w <- result.country[Signs == "result" & statistic %in% c("se", "sp")][order(Country)]

dt.bp <- dcast(w, statistic ~ Country, value.var="est")
dt.bp <- as.matrix(dt.bp, rownames=T)

ci.w <- 0.05

par(mar=c(2, 5, 2, 5), xpd=T)
bp <- barplot(dt.bp, ylab="Value", cex.names=0.8, ylim=c(0,1), beside=T, col=c("gray", "grey50"))

legend("right",
       legend = c("Sensibility", "Specificity"),
       col=c("gray", "grey50"),
       pch = 15,
       bty = "n",
       pt.cex = 2,
       cex = 0.7,
       horiz = F, inset = c(-0.15, 0))

bp <- as.vector(bp)
segments(bp-ci.w, w$lower, bp+ci.w, w$lower, lwd = 1.5)
segments(bp-ci.w, w$upper, bp+ci.w, w$upper, lwd = 1.5)
segments(bp, w$lower, bp, w$upper, lwd = 1.5)
```


### Result by Read Number

```{r, echo=F}
c <- dt.final[Signs == "result"][value != "Not readable"]
c <- dcast(c, `Patient ID`+ read_number ~ Readers, value.var = "value", fun.aggregate = unique, fill=NA)
c <- c[, .(`Patient ID`, read_number, Clinician, NationalReader)]


w <- lapply(unique(c$read_number), function(x){
  c <- c[read_number == x]
  c[, Clinician := factor(Clinician, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  c[, NationalReader := factor(NationalReader, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  table(c$Clinician, c$NationalReader)
})

w <- lapply(w, epi.tests, conf.level = 0.95, method = "clopper-pearson")
names(w) <- unique(c$read_number)


w <- lapply(w, function(x){
  as.data.table(x$detail)
})

w <- rbindlist(w, idcol = T)
```


```{r, echo=F}
w <- w[statistic %in% c("se", "sp")]
w %>% kable %>% kable_styling
```

```{r, echo=F}
dt.bp <- dcast(w, statistic ~ .id, value.var="est")
dt.bp <- as.matrix(dt.bp, rownames=T)

ci.w <- 0.05

par(mar=c(2, 5, 2, 5), xpd=T)
bp <- barplot(dt.bp, ylab="Value", cex.names=0.8, ylim=c(0,1), beside=T, col=c("gray", "grey50"))

legend("right",
       legend = c("Sensibility", "Specificity"),
       col=c("gray", "grey50"),
       pch = 15,
       bty = "n",
       pt.cex = 2,
       cex = 0.7,
       horiz = F, inset = c(-0.15, 0))

bp <- as.vector(bp)
segments(bp-ci.w, w$lower, bp+ci.w, w$lower, lwd = 1.5)
segments(bp-ci.w, w$upper, bp+ci.w, w$upper, lwd = 1.5)
segments(bp, w$lower, bp, w$upper, lwd = 1.5)
```


```{r}
dt.bp <- as.data.table(t(dt.bp))
dt.bp[, x := 1:4]

lm(dt.bp$se ~ dt.bp$x) %>% summary

lm(dt.bp$sp ~ dt.bp$x) %>% summary
```


### By read number and Country

```{r, echo=F}
dt.country.read <- dt.country[Signs != "result"] %>% dcast(`Patient ID`+ Country + read_number ~ Readers,
                                                           value.var = "value",
                                                           fun.aggregate = unique,
                                                           fill=NA)

dt.country.read <- dt.country.read %>% dcast(`Patient ID`+ Country + NationalReader ~ read_number,
                                             value.var = "Clinician",
                                             fun.aggregate = unique,
                                             fill=NA)

dt.country.read %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))
```

```{r, echo=F}
dt.country.read <- dt.country[Signs == "result"] %>% dcast(`Patient ID`+ Country + read_number ~ Readers,
                                                           value.var = "value",
                                                           fun.aggregate = unique,
                                                           fill=NA)
```



```{r, echo=F}
a <- dt.country.read[, .(Country, read_number)] %>% unique

list.tbl <- lapply(1:nrow(a), function(x){
  dt.temp <- dt.country.read[Country == a$Country[[x]] & read_number == a$read_number[[x]]]
  dt.temp[, Clinician := factor(Clinician, levels = rev(sort(unique(Clinician))))]
  dt.temp[, NationalReader := factor(NationalReader, levels = rev(sort(unique(NationalReader))))]
  table(dt.temp$Clinician, dt.temp$NationalReader)
})

list.tbl <- lapply(list.tbl, epi.tests, conf.level = 0.95, method = "clopper-pearson")

list.tbl <- lapply(list.tbl, function(x){ as.data.table(x$detail) })

result.country <- rbindlist(list.tbl)

result.country[, Country := rep(a$Country, each=18)]
result.country[, read_number := rep(a$read_number, each=18)]

result.country[, ci := paste(round(est, 2), " [", round(lower, 2), "-", round(upper, 2), "]", sep="")]

dcast(result.country, statistic + Country ~ read_number, value.var = "ci") %>% kable %>% kable_styling
```


```{r, echo=F}
result.country[statistic %in% c("se", "sp")] %>%
  ggplot( aes(x=read_number, y=est, fill=Country)) +
  geom_bar(position  = "dodge", stat = "identity") +
  geom_errorbar(aes(ymin=lower, ymax=upper), position  = "dodge") +
  ylab("value") +
  facet_wrap(~statistic)
```


#### Characteristic of FN and FP

```{r}
c <- dt.final[Signs != "result"]
c <- dcast(c, `Patient ID`+ Country + read_number + Signs ~ Readers, value.var = "value", fun.aggregate = unique, fill=NA)

c[Clinician == "Yes" & NationalReader == "No", Status := "FP"]
c[Clinician == "No" & NationalReader == "Yes", Status := "FN"]
```

```{r}
c %>%
  tbl_summary(
    include=-c(`Patient ID`, Clinician, NationalReader, SPI),
    by = Status,
    type = everything() ~ "categorical",
    statistic = all_categorical() ~ "{p} % ({n}/{N})",
    missing="ifany"
  ) %>% add_overall(last=T)
```

```{r}
c %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
  tbl_summary(
    include=-c(`Patient ID`, Clinician, NationalReader, SPI),
    by = Status,
    type = everything() ~ "categorical",
    statistic = all_categorical() ~ "{p} % ({n}/{N})",
    missing="ifany"
  ))
```

Caracteristiques des discordances :

```{r}
c[, signs.read := paste(Signs, read_number) %>% as.factor]

c <- c[order(signs.read)]

c %>%
  tbl_strata(
    strata = Country,
    .tbl_fun =
      ~ .x %>%
  tbl_summary(
    include=-c(`Patient ID`, Clinician, NationalReader, SPI, Signs, read_number),
    by = Status,
    type = everything() ~ "categorical",
    statistic = all_categorical() ~ "{p} % ({n}/{N})",
    missing="ifany"
  ))


c[Status %in% c("FP", "FN")] %>%
  tbl_summary(
    include=-c(`Patient ID`, Clinician, NationalReader, SPI, Signs, read_number),
    by = Country,
    type = everything() ~ "categorical",
    statistic = all_categorical() ~ "{p} % ({n}/{N})",
    missing="ifany"
  )
```


## National Reader versus SPI

### By signs

```{r, echo=F}
c <- dt.final[Signs != "quality"][value != "Not readable"]
c <- dcast(c, `Patient ID`+ Signs ~ Readers, value.var = "value", fun.aggregate = unique, fill=NA)
c <- c[, .(`Patient ID`, Signs, SPI, NationalReader)]
```

#### Contingency table

```{r, echo=F}
b <- c[Signs != "result"]

by.sign <- b %>%
  tbl_strata(
    strata = Signs,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))

all.sign <- b[, Signs:="All"] %>%
  tbl_strata(
    strata = Signs,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(
        include=-`Patient ID`,
        by = NationalReader,
        type = everything() ~ "categorical",
        statistic = all_categorical() ~ "{p} % ({n}/{N})",
        missing="ifany"
      ))

tbl_merge(list(all.sign, by.sign), tab_spanner = F)
```


#### Performances with epi package

```{r, echo=F}
c.sign <- c[Signs != "result"]
c.sign[, SPI := factor(SPI, levels=c("Yes", "No"))]
c.sign[, NationalReader := factor(NationalReader, levels=c("Yes", "No"))]

all.sign <- list(
  table(c.sign$NationalReader, c.sign$SPI)
  )

by.sign <- lapply(unique(c.sign$Signs), function(x){
  table(c.sign[Signs == x]$NationalReader, c.sign[Signs == x]$SPI)
})

result <- lapply("result", function(x){
  c <- c[Signs == x]
  c[, SPI := factor(SPI, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  c[, NationalReader := factor(NationalReader, levels=c("Suggestive of TB", "Not suggestive of TB"))]
  table(c$NationalReader, c$SPI)
})

b <- c(all.sign, by.sign, result)

names(b) <- c("All", unique(c.sign$Signs), "result")
```


```{r, echo=F}
b.res <- lapply(b, epi.tests, conf.level = 0.95, method = "clopper-pearson")

b.res <- lapply(b.res, function(x){
  q <- as.data.table(x$detail)
  q <- q[, lapply(.SD, round, 2), by= .(statistic)]
  q 
})

b.res <- lapply(b.res, function(x){
  x[, all := paste(est, " [", lower, "-", upper, "]", sep="")]
})


b.res <- rbindlist(b.res, idcol = T)

dcast(b.res, statistic ~ .id, value.var = "all") %>% kable %>% kable_styling
```

```{r}
c.res <- lapply(b, epi.kappa)

c.res <- lapply(c.res, rbindlist, fill=T, idcol="param")

c.res <- c.res %>% rbindlist(idcol=T) %>%
  .[param %in% c("pabak", "kappa")] %>%
  .[, .(.id, param, est = round(est, 2), lower = round(lower, 2), upper = round(upper, 2))]

c.res[, all := paste(est, " [", lower, "-", upper, "]", sep="")]

dcast(c.res, param ~ .id, value.var = "all") %>% kable %>% kable_styling
```



# Supplementary Tables


```{r}
dt.site <- fread("data/siteid.csv", encoding = "Latin-1", na.strings = "")

dt.decent <- fread("data/CRFDECENTRALIZATIONM_DATA_LABELS_2023-05-09_1244.csv", na.strings = "", encoding="Latin-1")

#library(REDCapR)
#dt.decent <- redcap_read(redcap_uri = "https://tb-speed.credim.u-bordeaux.fr/redcap_v13.1.16/API/",
#                          token = "7A2D04F0B8537C9350C43DE9FF92E618",
 #                         raw_or_label = "label")$data
#names(dt.decent)

dt.decent <- dt.decent[`Repeat Instrument` == "CHEST X-RAY", c(1, 36, 47)]

names(dt.decent) <- c("patid", "Not performed", "result")

dt.decent <- dt.decent[-which(`Not performed` == "Not performed / Não realizado / ??????????" & is.na(result))]

dt.decent[, result := factor(result)]

levels(dt.decent$result) <- c("Not readable", "Not suggestive", "Suggestive")

dt.decent[, Code := substr(patid, 3, 5)]

dt.decent <- dt.decent[dt.site, on ="Code"]

dt.recap <- dcast(dt.decent, Country + District ~ result)

dt.recap <- dt.decent[, .(Total = .N), by=.(Country, District)] %>%
  .[dt.recap, on=c("Country", "District")]

dt.recap[, Selected := Suggestive + `Not readable` + 0.1*`Not suggestive`]

Tot <- dt.recap[, lapply(.SD, sum), .SDcols=names(dt.recap[, -c("Country", "District")])]

dt.recap <- rbind(dt.recap, Tot, fill=T)
```

Nombre total de radios réalisées et sélectionnées pour l'étude :

```{r}
dt.recap %>% kable %>% kable_styling

sum(dt.recap$Total - dt.recap$`NA`)

#dt.decent[, .N, by=patid][N>1]
```

```{r}
dt.final.site <- dt.final[Signs == "result" & Readers == "Clinician"]
```


Nombre de radio revues dans le cadre de l'étude :

```{r}
dt.final.site <- dt.final.site %>% dcast(Country + DISTRICT ~ value, value.var="Patient ID")

Tot <- dt.final.site[, lapply(.SD, sum), .SDcols=names(dt.final.site[, -c("Country", "DISTRICT")])]

dt.final.site <- rbind(dt.final.site, Tot, fill=T)

dt.final.site[, Total := rowSums(dt.final.site[, -c("Country", "DISTRICT")])]

dt.final.site %>% kable %>% kable_styling
```


# Lexique

The following performance measures are returned:

Notation | Definition
--|--
tp | True prevalence
ap | Apparent prevalence
se | Diagnostic test sensitivity
sp | Diagnostic test specificity
diag.ac	| Diagnostic accuracy (the correctly classified proportion)
diag.or	| Diagnostic odds ratio
nndx | The number needed to diagnose
youden | Youden's index
pv.pos | Positive predictive value
pv.neg | Negative predictive value
lr.pos | Likelihood ratio of a positive test
lr.neg	| Likelihood ratio of a negative test
p.rout | The proportion of subjects with the outcome ruled out
p.rin	| The proportion of subjects with the outcome ruled in
p.tpdn | The proportion of true outcome negative subjects that test positive (false T+ proportion for D-)
p.tndp | The proportion of true outcome positive subjects that test negative (false T- proportion for D+)
p.dntp | The proportion of test positive subjects that are outcome negative (false T+ proportion for T+)
p.dptn | The proportion of test negative subjects that are outcome positive (false T- proportion for T-)

# Session info

```{r}
sessionInfo()
```


# References
